---
title: "ReSVidex report"
output: html_document
params:
  n: NA
---
This report was created using the **ReSVidex v`r packageVersion("resvidex")`** software for subtyping of RSV sequences.<br /> 


<h2>Run stats</h2>
Run was performed by user *`r input$user`* on `r Sys.Date()`.<br />
Input file *`r  values$SequenceData_FILE`* from which **`r as.character(length(data_reactive()$data_out$Label))`** sequences were selected for analysis.<br />

<h2>Output table</h2>
The following table lists the sequences under analysis that have passed the quality checks and the corresponding classification results. 
```{r,echo=FALSE, warning=FALSE,message=FALSE}
# The `params` object is available in the document.
 col<-"#7AC5CD"
      col2<-"#FF8C00"

      table<-table_pass()
 datatable(table,selection = 'single',
                style = 'bootstrap',
                extensions = 'Buttons',
                options = list(
                  columnDefs = list(list(targets = c(5,7,8), visible = FALSE)),
                  dom = 'Bfrtip',
                  lengthMenu = list(c(5, 15, -1), c('5', '15', 'All')),
                  pageLength = 15,
                  buttons =
                    list('copy', 'print', list(
                      extend = 'collection',
                      buttons = list(
                        list(extend = 'csv', filename = paste(input$file[1,1],"resvidex_results"),sep=""),
                        list(extend = 'excel', filename = paste(input$file[1,1],"resvidex_results"),sep=""),
                        list(extend = 'pdf', filename = paste(input$file[1,1],"resvidex_results"),sep="")),
                      text = 'Download'
                    ),
                    list(
                      extend = "collection",
                      text = 'Show All',
                      action = DT::JS("function ( e, dt, node, config ) {
                                    dt.page.len(-1);
                                    dt.ajax.reload();
                                }")
                    ))
                ))%>%formatStyle("Length","Length_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))%>%
        formatStyle("N","N_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))%>%
        formatStyle("Probability","Probability_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))

 
```
<h2>Output table</h2>
The following table lists the sequences under analysis that not have passed the quality checks.
```{r,echo=FALSE, warning=FALSE,message=FALSE}
# The `params` object is available in the document.
 col<-"#7AC5CD"
      col2<-"#FF8C00"

 table<-table_reject()


      datatable(table,selection = 'single',
                style = 'bootstrap',
                extensions = 'Buttons',
                options = list(
                  columnDefs = list(list(targets = c(5,7,8), visible = FALSE)),
                  dom = 'Bfrtip',
                  lengthMenu = list(c(5, 15, -1), c('5', '15', 'All')),
                  pageLength = 15,
                  buttons =
                    list('copy', 'print', list(
                      extend = 'collection',
                      buttons = list(
                        list(extend = 'csv', filename = paste(input$file[1,1],"resvidex_results"),sep=""),
                        list(extend = 'excel', filename = paste(input$file[1,1],"resvidex_results"),sep=""),
                        list(extend = 'pdf', filename = paste(input$file[1,1],"resvidex_results"),sep="")),
                      text = 'Download'
                    ),
                    list(
                      extend = "collection",
                      text = 'Show All',
                      action = DT::JS("function ( e, dt, node, config ) {
                                    dt.page.len(-1);
                                    dt.ajax.reload();
                                }")
                    ))
                ))%>%formatStyle("Length","Length_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))%>%
        formatStyle("N","N_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))%>%
        formatStyle("Probability","Probability_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))
 
```
<h2>

Classification models

</h2>

The following table lists the models used for the classification.

```{r,echo=FALSE, warning=FALSE,message=FALSE}


model1_data<-  info_model()


datatable(model1_data)
```
